---
title: "Notes from week 1, Wednesday--Thursday 4--5 April"
---

```{r, echo = FALSE}
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE)
```

# Intro to LSSS
___

## History of digital acoustics at Hafró

Simrad EK500 arrived on the scene at the start of the 1990s. We have a
historic collection of acoustic data starting in 1992. The data set in
the old format was moved from backup-tapes to portable hard disks and
stored on a net drive a few years back. Reduced resolution as compared
to more recent data.

We are in the process of setting up a comprehensive collection of
acoustics in the EK60 format, see ACDC-section.

The next generation of echosounders with broadband capabilities
produce more volumnious data than current systems, the diffrence can
be between 1 and 3 orders of magnitude (somewhere between 10 to a 1000
fold).

## History of acoustics data post-processing at Hafró

Simrad BI500 was the post-processing program shipped with the
EK500. Was developed further at IMR in Bergen as BEI, which Hafró
never took into use. Multi-frequency post-processing introduced with
KORONA close to the start of the new millenium. Collaboration between
IMR and CMR in Bergen in ~2007-2008 resulted in LSSS which Hafró took
into use in 2011 after a period of experimentation with EchoView
(without it being adopted for wholehearted use).

# Basic LSSS
___

Went trough basic workings of LSSS, showed how to set up the program
and set up a survey, demonstrated the functionality of tools in LSSS,
showed interpretations, saving to data base, report generations,
survey backup, ... .

# Scrutiny workshop
___

Participants started on interpretation of a winter capelin
survey. Practiced using LSSS. We did not reach the stage of comparing
results of all participants which might be tried for the next time
around.

# AC/DC or the Hafró ACoustic Data Collection

At the start of the workshop a script tallying the data was shown, here are the bare bones of script to document the data usage:

The libraries we use:

```{r}
library(tidyverse)
library(lubridate)
library(fs)
```

Collectiong the info from the file system, a little weighty operation, so I saved the results:

```{r}
#
#dir_info("/u5/bergmal/EK60raw", recursive = TRUE, glob = "*.raw") -> raw_files
#saveRDS(raw_files, "raw_files.rds")

raw_files <- readRDS("raw_files.rds")
```

The data that have been copied to the `/u5/bergmal/EK60raw` now amount to `r sum(raw_files$size)`.

Breakdown by year:

```{r}
raw_files %>%
  mutate(yyyy = year(modification_time)) %>%
  group_by(yyyy) %>%
  summarize(n = n(),
            tot_size = sum(size)) %>%
  mutate(avg_size = tot_size/n)
```


The raw file permissions status on the net, details on how to work with permissions to be added:

```{r}
raw_files %>% group_by(user, permissions) %>% summarize(n = n())
```

The daily collection on the two vessels (in the data on the net-drive) averages by year:

```{r}
raw_files %>%
  mutate(yyyy = year(modification_time),
         date = date(modification_time),
         ship = substring(path, 21, 21)) %>%
  group_by(yyyy, ship, date) %>%
  summarize(size = sum(size)) %>%
  summarize(avg_daily_size = mean(size)/(2^20)) %>%
  ggplot() +
    geom_line(aes(yyyy, avg_daily_size, colour = ship))
 ```
